---
title: "Creel survey data"
author: "John Phelan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 8)

library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(kableExtra)
library(data.table)
library(lubridate)
library(geosphere)
library(ggmap)
library(sqldf)
library(DBI)
source(here::here("scripts/utils/col_types_f.R"))

# onedrive_wd = paste0(str_extract(getwd(),"C:/Users/[A-Z]+/"),"OneDrive - Government of BC/R_projects/CultusData/")
# all_creel <- read_xlsx(paste0(onedrive_wd,"/data/Cultus_Lake_Creel_-_All_Query.xlsx"))

db_filepath <- "scripts/shiny/www/CultusData.sqlite"
con <- dbConnect(RSQLite::SQLite(), here::here(db_filepath))

# Find all tables with 'creel' in the name
creel_table_names <- dbGetQuery(con, "
  SELECT name 
  FROM sqlite_master 
  WHERE type='table' AND name LIKE '%creel%'
")$name

# Read each table into a list
creel_tables_list <- lapply(creel_table_names, function(tbl) {
  dbReadTable(con, tbl)
})

# Name the list elements by their corresponding table names
names(creel_tables_list) <- creel_table_names


surveyQuestionsAnswers <- merge(
  creel_tables_list$creelSurveyAnswers,
  creel_tables_list$creelSurveyQuestions,
  by.x = "Question",
  by.y = "questionID"
)

 
# Remove the two original tables from the list
creel_tables_list$creelSurveyAnswers <- NULL
creel_tables_list$creelSurveyQuestions <- NULL 


# Remove 'time' column from each table in the list, if it exists
creel_tables_list_cleaned <- lapply(creel_tables_list, function(df) {
  if ("time" %in% names(df)) {
    df <- select(df, -time)
  }
  df
})

# Perform full join across all cleaned tables
all_creel <- reduce(creel_tables_list_cleaned, full_join)


samples<- all_creel |> 
  filter(date == ("2023-07-02"))

results_2023<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  filter(date < as.Date("2024-01-01")) |> 
  summarize(not_na_count = sum(!is.na(spp)))

results_2024<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  filter(date >= as.Date("2024-01-01") & date <= as.Date("2025-01-01")) |> 
  summarize(not_na_count = sum(!is.na(spp)))  

results_2025<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  filter(date >= as.Date("2025-01-01") & date <= as.Date("2026-01-01")) |> 
  summarize(not_na_count = sum(!is.na(spp)))  


custom_theme <- theme(
  axis.title = element_text(face = "bold"),    # Make axis titles bold
  axis.text = element_text(face = "bold"),     # Make axis ticks bold
  legend.title = element_text(face = "bold"),  # Make legend title bold
  legend.text = element_text(face = "bold")    # Make legend labels bold
)

# surveyQuestionsAnswers |> 
#   filter(date >= as.Date("2025-01-01") & date <= as.Date("2026-01-01")) |>
#   filter(Question == 9) |> 
#   group_by(Answer) |> 
#   summarise(count = n())

```

## Preferred Fish species {.tabset}

In 2023, **`r results_2023$not_na_count`** anglers provided information about their target species. This number increased to **`r results_2024$not_na_count`** in 2024. 

### Preferred fish 2025 barchart 


```{r fish_2023}

fish_spp<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  filter(date > as.Date("2024-01-01") & date <= as.Date("2026-01-01")) |> 
  select(date, anglerID, spp, site, number_anglers, number_rods, total_person_hr_fished ,total_fish_caught , total_retained) 




spp_count <- fish_spp |> 
  mutate(spp = str_replace_all(spp, ";", ",")) |> 
  mutate(
    prefferedSpp = str_trim(spp),  # Remove leading/trailing spaces
    prefferedSpp = str_to_lower(spp),
    prefferedSpp = str_replace_all(spp,  # Correct specific typos
                                   c(
                                     "^trout$" = "trout",
                                     " northern pikeminow" = "northern pikeminnow",
                                     "trout " = "trout",
                                     "pikeminow" = "northern pikeminnow",
                                     "northern northern pikeminnow" = "northern pikeminnow",
                                     "typically fish salmon" = "salmon"))
  ) |> 
  separate_rows(spp, sep = ",") |>      # Handle multiple species in a single cell
  mutate(spp = str_trim(spp)) |> 
  filter(!is.na(spp) & spp != "") |> 
  count(spp, sort = TRUE)

spp_count_plot<- spp_count |> arrange(desc(n)) %>% 
  slice_head(n = 6) 

# Generate a vector of distinct colors, one for each species
species_colors <- RColorBrewer::brewer.pal(n = length(unique(spp_count_plot$spp)), name = "Dark2")


ggplot(spp_count_plot, aes(x = reorder(spp, n), y = n, fill = spp)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_flip() +
  labs(
    title = "Preferred Species",
    x = "Species",
    y = "Count"
  ) +
  scale_fill_manual(values = species_colors) +  # Use the manually assigned colors
  geom_text(aes(label = n), hjust = -0.2, size = 4, fontface = "bold") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12, face = "bold"),  # Bold x-axis text and ticks
    axis.text.y = element_text(size = 12, face = "bold"),  # Bold y-axis text and ticks
    axis.title.x = element_text(size = 14, face = "bold"),  # Larger and bold x-axis label
    axis.title.y = element_text(size = 14, face = "bold"),  # Larger and bold y-axis label
    plot.title = element_text(size = 16, face = "bold")
  )

```


### Fish species 2023 list

```{r fish_spp_23_list}

setDT(spp_count)
spp_count |> 
  rename(`Preferred species` = spp ) |> 
  kbl(caption = "Species targeted by anglers in 2025") |> 
   kable_classic(full_width = F, html_font = "Cambria")
  

```

## Angler Details {.tabset} 

This is a summary of the anglers, where they fished and with what gear was used in 2025


```{r angler_details}

angler_details <- all_creel %>%
  filter(date > as.Date("2025-01-01") & date <= as.Date("2026-01-01")) |> 
  group_by(date, surveyNumber) %>%
  summarise(
    site = first(site),
    residency = first(residency),
    numberAnglers = sum(as.numeric(number_anglers), na.rm = TRUE),
    numberRods = sum(as.numeric(number_rods), na.rm = TRUE),
    personHoursFished = sum(as.numeric(total_person_hr_fished), na.rm = TRUE),
    noAnglingBoats = sum(as.numeric(number_angling_boats), na.rm = TRUE),
    noBoatAnglers = sum(as.numeric(number_boat_anglers), na.rm = TRUE),
    noShoreAnglers = sum(as.numeric(number_shore_anglers), na.rm = TRUE),
    noDockAnglers = sum(as.numeric(number_shore_anglers), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(if_any(everything(), ~ !is.na(.)))

angling_months <- all_creel |> 
  filter(date > as.Date("2025-01-01") & date <= as.Date("2026-01-01")) |>
  mutate(date = as.Date(date)) |> 
  select(date, surveyNumber) |> 
  distinct(date, surveyNumber, .keep_all = TRUE)

```

### Site plot

```{r site_plot}

site_summary <- angler_details |> 
  mutate(site = str_replace_all(site, c(
    "3: Maple Bay" = "Maple Bay"
  ))) |> 
  mutate(site = str_replace_all(site, c(
    "Maple Bay" = "3: Maple Bay"
  ))) |> 
  group_by(site) |> 
  summarize(total_anglers = sum(as.numeric(numberAnglers), na.rm = TRUE), .groups = "drop") |> 
  filter(!is.na(site))

ggplot(site_summary, aes(x = site, y = total_anglers, fill = site)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Total Anglers per Site",
       x = "Site",
       y = "Total Anglers",
       fill = "Site") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  custom_theme



```


### Survey effort

```{r month_plot}

angling_months <- angling_months %>%
  mutate(MonthYear = floor_date(date, "month"))

monthly_counts <- angling_months %>%
  group_by(MonthYear) %>%
  summarise(Total = n())

ggplot(monthly_counts, aes(x = MonthYear, y = Total)) +
  geom_line() +
  geom_point() +  # Add points for clarity
  labs(x = "Month", y = "Total surveys", title = "Surveys completed by month") +
  theme_minimal() +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  custom_theme

```

### Gender and age of anglers

```{r}

test = all_creel

all_creel = all_creel |> 
  filter(date > as.Date("2025-01-01") & date <= as.Date("2026-01-01"))


demo <- all_creel |> 
  distinct(date, surveyNumber, .keep_all = TRUE) |> 
  select(gender, age_class) |> 
  filter(!is.na(age_class)) |> 
  complete(gender, age_class, fill = list(n = 0)) |> 
  filter(!is.na(gender))  # Remove NA from gender

ggplot(demo, aes(x = age_class, fill = gender)) +
  geom_bar(position = "dodge") +
  labs(x = "Age Class", y = "Count", fill = "Gender") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0, 250)+
  custom_theme


```



### Fishing methods

```{r fishing_methods}

# Prepare the data: summarize the methods of fishing
angler_details_summary <- angler_details %>%
  select(noAnglingBoats, noBoatAnglers, noShoreAnglers, noDockAnglers) %>%
  summarise(
    Boat_Anglers = sum(as.numeric(noBoatAnglers), na.rm = TRUE),
    Shore_Anglers = sum(as.numeric(noShoreAnglers), na.rm = TRUE),
    Dock_Anglers = sum(as.numeric(noDockAnglers), na.rm = TRUE)
  ) %>%
  pivot_longer(cols = everything(), names_to = "Fishing_Method", values_to = "Total_Anglers")

ggplot(angler_details_summary, aes(x = Fishing_Method, y = Total_Anglers, fill = Fishing_Method)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Fishing Methods and Total Anglers", 
       x = "Fishing Method", 
       y = "Total Anglers",
       fill = "Method") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  custom_theme
```

### Distance to Cultus lake


```{r cultus_distance}

distance_all<- all_creel |> 
  distinct(date, surveyNumber, .keep_all = TRUE) |> 
  select(city_prov_country, postal_code_first_3) |> 
  filter(if_any(everything(), ~ !is.na(.)))

postcodes<-distance_all[!is.na(distance_all$postal_code_first_3),]

cultus_loc <- c(lat = 49.067898710337715, lon = -121.97819734971488)


library(tidygeocoder)
library(dplyr)
library(stringr)

geocoded_postcodes <- postcodes |>
  distinct(postal_code_first_3) |>
  mutate(
    postCode = str_to_upper(postal_code_first_3)
  ) |>
  geocode(
    postCode,
    method = "osm",
    lat = lat,
    long = lon
  )

# geocoded_postcodes |> 
#   filter(is.na(lat) | is.na(lon)) |> 
#   print(n = Inf)

geocoded_postcodes <- geocoded_postcodes |> 
  filter(!is.na(lat))
# Calculate distances (in kilometers)
geocoded_postcodes <- geocoded_postcodes |> 
  mutate(
    distance_km = distHaversine(
      cbind(lon, lat),  # Coordinates of postal codes
      c(cultus_loc["lon"], cultus_loc["lat"])  # Coordinates of Cultus Lake
    ) / 1000  # Convert meters to kilometers
  )

```

There were **`r nrow(distance_all)`** responses that had either a location and/or a postcode included in the survey responses. Of those, **`r nrow(postcodes)`** post codes were supplied. **`r nrow(geocoded_postcodes)`** postcodes were found to be usable Canadian postcodes, which could be used to calculate a distance to Cultus lake. 


```{r distance_plots}

# ggplot(geocoded_postcodes, aes(x = distance_km)) +
#   geom_histogram(
#     binwidth = 100,  # Set bin width to 50 km
#     fill = "steelblue", 
#     color = "black"
#   ) +
#   labs(
#     title = "Histogram of Distances from Cultus Lake",
#     x = "Distance (km)",
#     y = "Count"
#   ) +
#   theme_minimal() +
#   scale_x_continuous(
#     breaks = seq(0, 12000, by = 500),
#     limits = c(0, 12000) 
#   ) +
#   theme(
#     plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
#     axis.title = element_text(size = 14, face = "bold"),
#     axis.text = element_text(size = 12),
#     axis.text.x = element_text(angle = 45, hjust = 1) 
#   )
```

```{r distance_table}

geocoded_postcodes <- geocoded_postcodes %>%
  mutate(distance_bin = cut(distance_km, 
                            breaks = c(seq(0, max(distance_km) - 50, by = 50), max(distance_km) + 1),  # Include the max value in the last bin
                            include.lowest = TRUE, 
                            right = FALSE,
                            labels = paste0(seq(0, max(distance_km) - 50, by = 50), 
                                            " - ", 
                                            seq(50, max(distance_km), by = 50))))

# Summarize the count of postal codes in each bin and filter out empty bins
distance_table <- geocoded_postcodes %>%
  group_by(distance_bin) %>%
  summarise(count = n(), .groups = "drop") %>%
  filter(count > 0) %>%
  arrange(distance_bin)

# Convert to data.table for better handling of table formatting
setDT(distance_table)

# Display the table using kableExtra
distance_table |> 
  rename(`distance to postcode` = distance_bin) |> 
  kbl(caption = "50km Distance Bins for Anglers") |> 
  kable_classic(full_width = F, html_font = "Cambria")

```



### Caught vs retained

Fish that were caught were not kept! Only some fish are being retained.

```{r caught_vs retained}

caught_retained <- all_creel[, grep("(_c|_r|_caught|_retained)$", names(all_creel))]



caught_retained <- caught_retained |> 
  filter(if_any(everything(), ~ !is.na(.)))
  




caught_retained <- all_creel |>
  select(matches("^number_.*_(c|r)$"))


caught_retained <- caught_retained |>
  filter(if_any(everything(), ~ !is.na(.)))


caught_retained <- caught_retained |>
  mutate(across(everything(), as.numeric))


# caught_retained_selected <- caught_retained %>%
#   select(starts_with("No") & (ends_with("r") | ends_with("c")))


caught_retained_long <- caught_retained |>
  pivot_longer(
    cols = everything(),
    names_to = c("Species", "Type"),
    names_pattern = "^number_(.*)_(c|r)$",
    values_to = "Count"
  ) |>
  filter(!is.na(Count))



caught_retained_summarized <- caught_retained_long |>
  complete(Species, Type = c("c", "r"), fill = list(Count = 0)) |>
  group_by(Species, Type) |>
  summarise(Total = sum(Count), .groups = "drop")



caught_retained_summarized <- caught_retained_summarized |>
  mutate(
    Species = recode(Species,
      ko = "Kokanee salmon",
      ct = "Cutthroat trout",
      bt = "Bull trout",
      lt = "Lake trout",
      rb = "Rainbow trout",
      other_spp = "Other species",
      pikeminnow = "Northern pikeminnow",
      smb = "Smallmouth bass"
    )
  )



ggplot(caught_retained_summarized,
       aes(x = Species, y = Total, fill = Type)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.6) +
  scale_fill_manual(
    values = c(c = "purple", r = "blue"),
    labels = c(c = "Caught", r = "Retained"),
    name = "Type"
  ) +
  labs(
    x = "Species",
    y = "Total Count"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) 

```





