---
title: "Creel survey data"
author: "John Phelan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 8)

library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
library(tidyr)
library(stringr)
library(kableExtra)
library(data.table)
library(lubridate)
library(geosphere)
library(ggmap)

onedrive_wd = paste0(str_extract(getwd(),"C:/Users/[A-Z]+/"),"OneDrive - Government of BC/R_projects/CultusData/")
all_creel <- read_xlsx(paste0(onedrive_wd,"/data/Cultus_Lake_Creel_-_All_Query.xlsx"))

results_2023<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  filter(date < as.Date("2024-01-01")) |> 
  summarize(not_na_count = sum(!is.na(prefferedSpp)))

results_2024<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  filter(date >= as.Date("2024-01-01")) |> 
  summarize(not_na_count = sum(!is.na(prefferedSpp)))  

custom_theme <- theme(
  axis.title = element_text(face = "bold"),    # Make axis titles bold
  axis.text = element_text(face = "bold"),     # Make axis ticks bold
  legend.title = element_text(face = "bold"),  # Make legend title bold
  legend.text = element_text(face = "bold")    # Make legend labels bold
)

```

## Preferred Fish species {.tabset}

In 2023, **`r results_2023$not_na_count`** anglers provided information about their target species. This number increased to **`r results_2024$not_na_count`** in 2024. 

### Preferred fish 2023 barchart 


```{r fish_2023}

fish_spp2023<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  subset(date < as.Date("2024-01-01")) |> 
  select(date, anglerID, prefferedSpp, site, numberAnglers, numberRods, personHoursFished,totFishCaught , totRetained) 




species_count_2023 <- fish_spp2023 |> 
  mutate(prefferedSpp = str_replace_all(prefferedSpp, ";", ",")) |> 
  mutate(
    prefferedSpp = str_trim(prefferedSpp),  # Remove leading/trailing spaces
    prefferedSpp = str_to_lower(prefferedSpp),
    prefferedSpp = str_replace_all(prefferedSpp,  # Correct specific typos
                                   c(
                                     "^trout$" = "trout",
                                     " northern pikeminow" = "northern pikeminnow",
                                     "trout " = "trout",
                                     "pikeminow" = "northern pikeminnow",
                                     "northern northern pikeminnow" = "northern pikeminnow",
                                     "typically fish salmon" = "salmon"))
  ) |> 
  separate_rows(prefferedSpp, sep = ",") |>      # Handle multiple species in a single cell
  mutate(prefferedSpp = str_trim(prefferedSpp)) |> 
  filter(!is.na(prefferedSpp) & prefferedSpp != "") |> 
  count(prefferedSpp, sort = TRUE)

species_23_plot<- species_count_2023 |> arrange(desc(n)) %>% 
  slice_head(n = 6) 

# Generate a vector of distinct colors, one for each species
species_colors <- RColorBrewer::brewer.pal(n = length(unique(species_23_plot$prefferedSpp)), name = "Dark2")


ggplot(species_23_plot, aes(x = reorder(prefferedSpp, n), y = n, fill = prefferedSpp)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_flip() +
  labs(
    title = "Preferred Species: 2023",
    x = "Species",
    y = "Count"
  ) +
  scale_fill_manual(values = species_colors) +  # Use the manually assigned colors
  geom_text(aes(label = n), hjust = -0.2, size = 4, fontface = "bold") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12, face = "bold"),  # Bold x-axis text and ticks
    axis.text.y = element_text(size = 12, face = "bold"),  # Bold y-axis text and ticks
    axis.title.x = element_text(size = 14, face = "bold"),  # Larger and bold x-axis label
    axis.title.y = element_text(size = 14, face = "bold"),  # Larger and bold y-axis label
    plot.title = element_text(size = 16, face = "bold")
  )

```


### Preferred fish 2024 barchart



```{r fish_2024}

fish_spp2024<- all_creel |> 
  mutate(date = as.Date(date)) |> 
  subset(date >= as.Date("2024-01-01")) |> 
  select(date, anglerID, prefferedSpp, site, numberAnglers, numberRods, personHoursFished,totFishCaught , totRetained)

species_count_2024 <- fish_spp2024 |> 
  mutate(
    # Replace semicolons and "and/or" with commas
    prefferedSpp = str_replace_all(prefferedSpp, ";|\\band\\b|\\bor\\b", ","),
    # Clean up spaces and convert to lowercase
    prefferedSpp = str_trim(str_to_lower(prefferedSpp))
  ) |> 
  # Split rows by commas
  separate_rows(prefferedSpp, sep = ",") |> 
  mutate(
    # Trim whitespace again after splitting
    prefferedSpp = str_trim(prefferedSpp),
    # Correct specific typos and normalize values
    prefferedSpp = str_replace_all(prefferedSpp, c(
      "^trout$" = "trout",
      "northern pikeminow" = "northern pikeminnow",
      "trout " = "trout",
      "pikeminow" = "northern pikeminnow",
      "northern northern pikeminnow" = "northern pikeminnow",
      "typically fish salmon" = "salmon",
      "smb" = "smallmouth bass",
      "\\b(any|any kind|anythingthing)\\b" = "anything",
      "\\bbass\\b" = "smallmouth bass",
      "pike" = "northern pikeminnow",
      "troutor" = "trout",
      "smallmouth smallmouth bass" = "smallmouth bass",
      "northern pikeminnowminn" = "northern pikeminnow",
      "but whatever is in" = "anything",
      "\\b(not an angler|not anglers|non-anglers)\\b" = "non-angler",
      "pileminnow" = "northern pikeminnow",
      "ps" = "pumpkinseed",
      "suckers" = "sucker",
      "\\b(rb|rt)\\b" = "rainbow trout",
      "notrouthern pikeminnow" = "northern pikeminnow",
      "ct" = "cutthroat trout"
    ))
  ) |> 
  # Filter out NA and empty strings
  filter(!is.na(prefferedSpp) & prefferedSpp != "") |> 
  # Count occurrences, sorted
  count(prefferedSpp, sort = TRUE)

# Exclude "non-angler" temporarily for the plot
species_24_plot_filtered <- species_count_2024 |> 
  filter(prefferedSpp != "non-angler") |> 
  arrange(desc(n)) |> 
  slice_head(n = 6)  # Keep the top 6 species

# Generate a vector of distinct colors, one for each species
species_colors <- RColorBrewer::brewer.pal(n = length(unique(species_24_plot_filtered$prefferedSpp)), name = "Dark2")

# Plot without "non-angler"
ggplot(species_24_plot_filtered, aes(x = reorder(prefferedSpp, n), y = n, fill = prefferedSpp)) +
  geom_bar(stat = "identity", show.legend = FALSE) +
  coord_flip() +
  labs(
    title = "Preferred Species: 2024",
    x = "Species",
    y = "Count"
  ) +
  scale_fill_manual(values = species_colors) +  # Use the manually assigned colors
  geom_text(aes(label = n), hjust = -0.2, size = 4, fontface = "bold") + 
  theme_minimal() +
  theme(
    axis.text.x = element_text(size = 12, face = "bold"),  # Bold x-axis text and ticks
    axis.text.y = element_text(size = 12, face = "bold"),  # Bold y-axis text and ticks
    axis.title.x = element_text(size = 14, face = "bold"),  # Larger and bold x-axis label
    axis.title.y = element_text(size = 14, face = "bold"),  # Larger and bold y-axis label
    plot.title = element_text(size = 16, face = "bold")
  )

```



### Fish species 2023 list

```{r fish_spp_23_list}

setDT(species_count_2023)
species_count_2023 |> 
  rename(`Preferred species` = prefferedSpp ) |> 
  kbl(caption = "Species targeted by anglers in 2023") |> 
   kable_classic(full_width = F, html_font = "Cambria")
  

```

### Fish epcies 2024 list

```{r fish_spp_24_list}
setDT(species_count_2024)
species_count_2024 |> 
  rename(`Preferred species` = prefferedSpp ) |> 
  kbl(caption = "Species targeted by anglers in 2024") |> 
   kable_classic(full_width = F, html_font = "Cambria")
```

## Angler Details {.tabset} 

This is a summary of the anglers, where they fished and with what gear was used for both years combined.


```{r angler_details}

angler_details <- all_creel %>%
  group_by(date, surveyNumber) %>%
  summarise(
    site = first(site),
    residency = first(residency),
    numberAnglers = sum(as.numeric(numberAnglers), na.rm = TRUE),
    numberRods = sum(as.numeric(numberRods), na.rm = TRUE),
    personHoursFished = sum(as.numeric(personHoursFished), na.rm = TRUE),
    noAnglingBoats = sum(as.numeric(noAnglingBoats), na.rm = TRUE),
    noBoatAnglers = sum(as.numeric(noBoatAnglers), na.rm = TRUE),
    noShoreAnglers = sum(as.numeric(noShoreAnglers), na.rm = TRUE),
    noDockAnglers = sum(as.numeric(noDockAnglers), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  filter(if_any(everything(), ~ !is.na(.)))

angling_months <- all_creel |> 
  mutate(date = as.Date(date)) |> 
  select(date, surveyNumber) |> 
  distinct(date, surveyNumber, .keep_all = TRUE)

```

### Site plot

```{r site_plot}

site_summary <- angler_details |> 
  mutate(site = str_replace_all(site, c(
    "3: Maple Bay" = "Maple Bay"
  ))) |> 
  mutate(site = str_replace_all(site, c(
    "Maple Bay" = "3: Maple Bay"
  ))) |> 
  group_by(site) |> 
  summarize(total_anglers = sum(as.numeric(numberAnglers), na.rm = TRUE), .groups = "drop") |> 
  filter(!is.na(site))

  ggplot(site_summary, aes(x = site, y = total_anglers, fill = site)) +
    geom_bar(stat = "identity") +
    theme_minimal() +
    scale_fill_brewer(palette = "Dark2") +
    labs(title = "Total Anglers per Site",
         x = "Site",
         y = "Total Anglers",
         fill = "Site") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))+
    custom_theme



```


### Survey effort

```{r month_plot}

angling_months <- angling_months %>%
  mutate(MonthYear = floor_date(date, "month"))

monthly_counts <- angling_months %>%
  group_by(MonthYear) %>%
  summarise(Total = n())

ggplot(monthly_counts, aes(x = MonthYear, y = Total)) +
  geom_line() +
  geom_point() +  # Add points for clarity
  labs(x = "Month", y = "Total surveys", title = "Surveys completed by month") +
  theme_minimal() +
  scale_x_date(date_labels = "%b %Y", date_breaks = "1 month") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  custom_theme

```

### Gender and age of anglers

```{r}

demo <- all_creel |> 
  distinct(date, surveyNumber, .keep_all = TRUE) |> 
  select(gender, AgeClass) |> 
  filter(!is.na(AgeClass)) |> 
  complete(gender, AgeClass, fill = list(n = 0)) |> 
  filter(!is.na(gender))  # Remove NA from gender

ggplot(demo, aes(x = AgeClass, fill = gender)) +
  geom_bar(position = "dodge") +
  labs(x = "Age Class", y = "Count", fill = "Gender") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0, 250)+
  custom_theme


```



### Fishing methods

```{r fishing_methods}

# Prepare the data: summarize the methods of fishing
angler_details_summary <- angler_details %>%
  select(noAnglingBoats, noBoatAnglers, noShoreAnglers, noDockAnglers) %>%
  summarise(
    Boat_Anglers = sum(as.numeric(noBoatAnglers), na.rm = TRUE),
    Shore_Anglers = sum(as.numeric(noShoreAnglers), na.rm = TRUE),
    Dock_Anglers = sum(as.numeric(noDockAnglers), na.rm = TRUE)
  ) %>%
  pivot_longer(cols = everything(), names_to = "Fishing_Method", values_to = "Total_Anglers")

ggplot(angler_details_summary, aes(x = Fishing_Method, y = Total_Anglers, fill = Fishing_Method)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") +
  labs(title = "Fishing Methods and Total Anglers", 
       x = "Fishing Method", 
       y = "Total Anglers",
       fill = "Method") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  custom_theme
```


### Visitor vs resident

From both years, there were 264 recorded for the residency of the anglers.  

```{r residency_plot}

angler_residency <- angler_details |> 
  filter(if_any(everything(), ~ !is.na(.))) |> 
  filter(!is.na(residency)) |> 
  mutate(residency = recode(residency, 
                            "Residency" = "Resident"))

# Plotting the data
ggplot(angler_residency, aes(x = residency)) +
  geom_bar(fill = "steelblue") +
  geom_text(stat = "count", aes(label = ..count..), vjust = -0.5, color = "black", fontface = "bold") +
  labs(title = "Distribution of Residency",
       x = "Residency",
       y = "Count") +
  theme_minimal() +
  custom_theme


```

### Distance to Cultus lake


```{r cultus_distance}

distance_all<- all_creel |> 
  distinct(date, surveyNumber, .keep_all = TRUE) |> 
  select(cityProvinceCountry, postCode) |> 
  filter(if_any(everything(), ~ !is.na(.)))

postcodes<-distance_all[!is.na(distance_all$postCode),]

cultus_loc <- c(lat = 49.067898710337715, lon = -121.97819734971488)


geocoded_postcodes <- postcodes |> 
  distinct(postCode) |>  # Only geocode unique postal codes
  mutate(
    postCode = str_to_upper(postCode),  # Capitalize postal codes
    geocode_result = map(postCode, ~ geocode(.x, output = "latlona")),
    lat = map_dbl(geocode_result, "lat"),
    lon = map_dbl(geocode_result, "lon")
  )

# geocoded_postcodes |> 
#   filter(is.na(lat) | is.na(lon)) |> 
#   print(n = Inf)

geocoded_postcodes <- geocoded_postcodes |> 
  filter(!is.na(lat))
# Calculate distances (in kilometers)
geocoded_postcodes <- geocoded_postcodes |> 
  mutate(
    distance_km = distHaversine(
      cbind(lon, lat),  # Coordinates of postal codes
      c(cultus_loc["lon"], cultus_loc["lat"])  # Coordinates of Cultus Lake
    ) / 1000  # Convert meters to kilometers
  )

```

There were **`r nrow(distance_all)`** responses that had either a location and/or a postcode included in the survey responses. Of those, **`r nrow(postcodes)`** post codes were supplied. **`r nrow(geocoded_postcodes)`** postcodes were found to be usable Canadian postcodes, which could be used to calculate a distance to Cultus lake. 


```{r distance_plots}

# ggplot(geocoded_postcodes, aes(x = distance_km)) +
#   geom_histogram(
#     binwidth = 100,  # Set bin width to 50 km
#     fill = "steelblue", 
#     color = "black"
#   ) +
#   labs(
#     title = "Histogram of Distances from Cultus Lake",
#     x = "Distance (km)",
#     y = "Count"
#   ) +
#   theme_minimal() +
#   scale_x_continuous(
#     breaks = seq(0, 12000, by = 500),
#     limits = c(0, 12000) 
#   ) +
#   theme(
#     plot.title = element_text(size = 16, face = "bold", hjust = 0.5),
#     axis.title = element_text(size = 14, face = "bold"),
#     axis.text = element_text(size = 12),
#     axis.text.x = element_text(angle = 45, hjust = 1) 
#   )
```

```{r distance_table}

geocoded_postcodes <- geocoded_postcodes %>%
  mutate(distance_bin = cut(distance_km, 
                            breaks = c(seq(0, max(distance_km) - 50, by = 50), max(distance_km) + 1),  # Include the max value in the last bin
                            include.lowest = TRUE, 
                            right = FALSE,
                            labels = paste0(seq(0, max(distance_km) - 50, by = 50), 
                                            " - ", 
                                            seq(50, max(distance_km), by = 50))))

# Summarize the count of postal codes in each bin and filter out empty bins
distance_table <- geocoded_postcodes %>%
  group_by(distance_bin) %>%
  summarise(count = n(), .groups = "drop") %>%
  filter(count > 0) %>%
  arrange(distance_bin)

# Convert to data.table for better handling of table formatting
setDT(distance_table)

# Display the table using kableExtra
distance_table |> 
  rename(`distance to postcode` = distance_bin) |> 
  kbl(caption = "50km Distance Bins for Anglers") |> 
  kable_classic(full_width = F, html_font = "Cambria")

```



### Caught vs retained

Fish that were caught were not kept! Only some fish are being retained.

```{r caught_vs retained}

caught_retained<- all_creel[, grep("^No.*[rc]$", names(all_creel))] 

caught_retained <- cbind(caught_retained, 
                         all_creel[, c("totRetained", "totFishCaught")])

caught_retained <- caught_retained |> 
  filter(if_any(everything(), ~ !is.na(.)))
  

caught_retained <- caught_retained |> 
  mutate(across(ends_with("c"), as.numeric)) |> 
  mutate(across(ends_with("r"), as.numeric))

caught_retained_selected <- caught_retained %>%
  select(starts_with("No") & (ends_with("r") | ends_with("c")))

caught_retained_long <- caught_retained_selected %>%
  pivot_longer(cols = everything(),
               names_to = c("Species", "Type"),
               names_pattern = "(No.*)(r|c)",
               values_to = "Count") %>%
  filter(!is.na(Count))

caught_retained_summarized <- caught_retained_long %>%
  complete(Species, Type = c("r", "c"), fill = list(Count = 0)) %>%
  group_by(Species, Type) %>%
  summarise(Total = sum(Count, na.rm = TRUE), .groups = "drop")

caught_retained_summarized<- caught_retained_summarized |> 
  mutate(Species = str_replace_all(Species, c(
    "NoKO" = "Kokanee salmon",
    "NoCT" = "Cutthroat trout",
    "NoBT" = "Bull trout",
    "NoLT" = "Lake trout",
    "NoRB" = "Rainbow trout",
    "NoOtherSpp" = "Other species",
    "Nopikeminnow" = "Northern pikeminnow",
    "NoSMB" = "Smallmouth bass"
  )))


ggplot(caught_retained_summarized, aes(x = Species, y = Total, fill = Type)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.35) +  # Set bar width here
  labs(x = "Species", y = "Total Count", fill = "Type") +
  theme_minimal() +
  #scale_fill_brewer(palette = "Dark2") +
  scale_fill_manual(values = c("r" = "blue", "c" = "purple"), labels = c("Caught", "Retained")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  custom_theme

```


### Caught vs retained - totals

```{r caught_retained_totals}
summary_data <- caught_retained |> 
  mutate(totRetained = as.numeric(totRetained),
         totFishCaught = as.numeric(totFishCaught)) |> 
  summarise(
    TotalRetained = sum(totRetained, na.rm = TRUE),
    TotalCaught = sum(totFishCaught, na.rm = TRUE)
  )

summary_long <- summary_data %>%
  gather(key = "Type", value = "Total", TotalRetained, TotalCaught) %>%
  mutate(Type = recode(Type, TotalRetained = "Retained", TotalCaught = "Caught"))

ggplot(summary_long, aes(x = Type, y = Total, fill = Type)) +
  geom_bar(stat = "identity", width = 0.35) +
  geom_text(aes(label = round(Total)), vjust = -0.5, size = 5) +  # Add text labels
  labs(x = "Type", y = "Total Count", fill = "Type") +
  theme_minimal() +
  scale_fill_brewer(palette = "Dark2") +
  theme(axis.text.x = element_text(angle = 0, hjust = 1))+
  custom_theme

```



