---
title: "Cultus lake suppression"
author: "John Phelan"
date: "2025-02-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(tidyverse)
library(DBI)
library(RSQLite)
library(sf)
library(osmdata)
library(knitr)
library(kableExtra)
library(patchwork)
library(bcdata)

```

# Cultus Lake data exploration {.tabset}

```{r load_data}

db_filepath = "scripts/shiny/www/CultusData.sqlite"

con<-dbConnect(RSQLite::SQLite(), db_filepath,extended_types = TRUE)

DBI::dbListTables(con)



```

## Abundance Capture data {.tabset}



```{r explore_abundance_capture}

query <- "SELECT * FROM abundanceCapture"
dbExecute(con = con, query)
#querydelete<-"DROP TABLE surveyData"
result <- dbSendQuery(conn = con, query)
abundance<-fetch(result, -1)
dbClearResult(result)

 
#get males and females
abundanceMF <- abundance |> 
  filter(sex == "M" | sex == "F")

# get undetermined
abundanceU<- abundance |> 
  filter(sex == "U" | is.na(sex)) |> 
  mutate(sex = "U")





```

### Seconds of Electricity used

```{r plot_elect}
ggplot(data = abundance) +
  geom_histogram(aes(secondsElectricity), bins = 30, fill = "steelblue", color = "black", alpha = 0.7) +
  labs(
    title = "Distribution of Seconds Electricity",
    x = "Seconds of Electricity Used",
    y = "Count"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold")
  )

```

### Number fish per day

```{r plot_fishPerDay}
# get the number of fish got in abundance per day
fishPerDay <- abundance |> 
  filter(date >= "2024-01-01",
         !is.na(secondsElectricity)) |> 
  group_by(date) |> 
  summarise(total_fish = n())

# plot this
p1<-ggplot(data = fishPerDay) +
  geom_bar(aes(x = date, y = total_fish), stat = "identity", fill = "steelblue", color = "black", alpha = 0.7) +
  labs(
    title = "Number of Fish Captured per Day",
    x = "Date",
    y = "Total Fish Captured"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text = element_text(size = 12),
    axis.title = element_text(size = 14, face = "bold")
  )

#save to ./images
ggsave("./images/abundance_fishPerDay.jpg", plot = p1, width = 10, height = 6)
```



### Males vs females and unsexed fish

The proportion of males/females and unsexed captured. Split by the method of capture. A, E and F. 
```{r plot MvFvU}
sexed<-ggplot(data = abundanceMF) +
  geom_histogram(aes(length, colour = sex, fill = sex), position = "identity",  alpha = 0.4)+
  ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  #facet_wrap(~ Method)+
  facet_grid(~ Method)+
  theme_minimal()

unsexed<-ggplot(data = abundanceU)+
  geom_histogram(aes(length, fill = sex), alpha = 0.4)+
  ggtitle(paste0("Percentage of unsexed fish: ",(round(nrow(abundanceU)/nrow(abundance)*100, 2))))+
  scale_fill_manual(values = "blue")+
  facet_grid(~ Method)+
  theme_minimal()

sexed + unsexed

```




## Angling data - Basok {.tabset}

```{r explore_AnglingBasok}


query <- "SELECT * FROM anglingCapBasok"
dbExecute(con = con, query)
#querydelete<-"DROP TABLE surveyData"
result <- dbSendQuery(conn = con, query)
angBas<-fetch(result, -1)
dbClearResult(result)

summary(angBas)

```


### Fish length

```{r length_basok}

ggplot(angBas)+
  geom_histogram(aes(length), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  facet_wrap(~ location)+
  theme_minimal()

```

### Fish weight

```{r weight_basok}
ggplot(angBas)+
  geom_histogram(aes(weight), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  facet_wrap(~ location)+
  theme_minimal()
```




## Angling derby data {.tabset}

```{r explore_anglingDerby}

query <- "SELECT * FROM anglingDerby"
dbExecute(con = con, query)
#querydelete<-"DROP TABLE surveyData"
result <- dbSendQuery(conn = con, query)
angDerby<-fetch(result, -1)
dbClearResult(result)



ggplot(angDerby)+
  geom_histogram(aes(length), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  facet_wrap(~ location)+
  theme_minimal()

ggplot(angDerby)+
  geom_histogram(aes(weight), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  facet_wrap(~ location)+
  theme_minimal()

```

### Length of fish from Angling derby


```{r L_derby}

length<-ggplot(angDerby)+
  geom_histogram(aes(length), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  facet_wrap(~ location)+
  theme_minimal()

length 

```

### Weight of fish from Angling derby

```{r}
weight<-ggplot(angDerby)+
  geom_histogram(aes(weight), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  facet_wrap(~ location)+
  theme_minimal()
```


## Nest Data {.tabset}

```{r explore_nestRaw }

query <- "SELECT * FROM nestRaw"
dbExecute(con = con, query)
#querydelete<-"DROP TABLE surveyData"
result <- dbSendQuery(conn = con, query)
nestRaw<-fetch(result, -1)
dbClearResult(result)


nestRaw<- nestRaw |> 
  mutate(lifeStage = if_else(lifeStage == "n/a", "N", lifeStage),
         lifeStage = if_else(lifeStage == "no", "N", lifeStage),
         lifeStage = if_else(lifeStage == "empty", "N", lifeStage),
         lifeStage = if_else(is.na(lifeStage), "N", lifeStage)
         )



test<-nestRaw |> 
  mutate(activityCompleted = str_replace(activityCompleted, "\\.\\.","\\."),
         activityCompleted = str_replace(activityCompleted, "\\.*",""),
         activityCompleted = str_replace(activityCompleted, "\\. \\.*","\\."),
         trimws(activityCompleted)
         )




```

### Nest depth

```{r nestDepth}
ggplot(nestRaw)+
  geom_histogram(aes(depth), position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  theme_minimal()
```

### Guarding males on nests

```{r guarding}
ggplot(nestRaw)+
    geom_histogram(aes(guarding), stat = "count", position = "identity",  alpha = 0.4)+
  #ggtitle(paste0("Percentage of sexed fish: ",(round(nrow(abundanceMF)/nrow(abundance)*100, 2))))+
  theme_minimal()

```

### Life stages seen at the nests

```{r lifeStages}
ggplot(nestRaw)+
  geom_bar(aes(lifeStage))+
  theme_minimal()

```

### What was done to the nests?

```{r activities}
ggplot(nestRaw)+
  geom_bar(aes(activityCompleted))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```




## Recapture Data {.tabset}

```{r explore_recapture}
query <- "SELECT * FROM recapture"
dbExecute(con = con, query)
#querydelete<-"DROP TABLE surveyData"
result <- dbSendQuery(conn = con, query)
recap<-fetch(result, -1)
dbClearResult(result)

recap <- recap |>
  mutate(startTime = hms::parse_hm(startTime),
         endTime = hms::parse_hm(endTime),
         hours_fished = as.numeric(difftime(endTime, startTime, units = "hours")))

recap_counts <- recap |> 
  group_by(date, location) |> 
  summarise(fish_caught = n())




```

### Length vs Weight

```{r length vs weight}
ggplot(data = recap)+
  geom_point(aes(x = weight, y= length))
```

### Histogram - length

```{r lengthHist}
ggplot(recap, aes(x = length)) +
  geom_histogram(binwidth = 10, fill = "blue", alpha = 0.5, boundary = 0) +
  scale_x_continuous(breaks = seq(0, max(recap$length, na.rm = TRUE), by = 50)) +
  theme_minimal() +
  labs(title = "Distribution of Fish Length", x = "Length (mm)", y = "Count")
```

### Histogram - weight

```{r weightHist}
ggplot(recap, aes(x = weight)) +
  geom_histogram(binwidth = 50, fill = "blue", alpha = 0.5, boundary = 0) +
  scale_x_continuous(breaks = seq(0, max(recap$weight, na.rm = TRUE), by = 50)) +
  theme_minimal() +
  labs(title = "Distribution of Fish Weight", x = "Weight (g)", y = "Count")
```

### Catch per location

```{r catchLocation}
ggplot(recap, aes(x = location)) +
  geom_bar(fill = "steelblue") +
  theme_minimal() +
  labs(title = "Number of Fish Caught per Location", x = "Location", y = "Count")

```

### Date vs fish caught

```{r fishCaught}
ggplot(recap, aes(x = length, y = weight)) +
  geom_point(alpha = 0.6) +
  theme_minimal() +
  labs(title = "Fish Length vs. Weight",
       x = "Length (mm)",
       y = "Weight (g)")
```




## Tag Data {.tabset}

```{r explore_tags}

query <- "SELECT * FROM tagData"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
tags<-fetch(result, -1)
dbClearResult(result)


tags_sf <- sf::st_as_sf(tags, coords = c("longitude", "latitude"), crs = 4326)

#tags_sf<-st_make_valid(tags_sf)
bc<-bcmaps::bc_bound()



tags_grouped <- tags_sf |> 
  group_by(stationName) |> 
  summarise(n = n())

cultus_bbox<-st_bbox(tags_grouped)


waterbodies<-readRDS("./data/named_lakes_and_rivers.rds")
cultus<-waterbodies[waterbodies$waterbody == "Cultus Lake",]
cultus<-cultus[1,]
buffered_cultus <- st_buffer(cultus, dist = 1000)  
bbox <- st_bbox(buffered_cultus)



tags$hour <- hour(hms(tags$time))



```

### Detections by station 

```{r}

stationLocs<-ggplot()+
  geom_sf(data = cultus, color = "darkgrey", fill = NA)+
  geom_sf(data = tags_grouped, aes(size = n, colour = stationName), inherit.aes = FALSE)+
  # geom_text(data = tags_grouped, aes(label = n, geometry = geometry), 
  #           stat = "sf_coordinates", nudge_y = 200, size = 3) + 
  coord_sf(xlim = c(bbox["xmin"], bbox["xmax"]), ylim = c(bbox["ymin"], bbox["ymax"])) +
  theme_minimal()

detecByLoc<-tags_sf |> 
  count(stationName) |> 
  ggplot(aes(x = reorder(stationName, -n), y = n)) +
  geom_col(fill = "steelblue", color = "black") +
  theme_minimal() +
  labs(title = "Detection Counts at Stations", x = "Stations", y = "Count") +
  coord_flip()

stationLocs 

detecByLoc

```

### Detections by date

```{r detecDates}
ggplot(tags, aes(x = as.Date(date))) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "black") +
  theme_minimal() +
  labs(title = "Detections Over Time", x = "Date", y = "Count")

```

### Detections by hour

```{r detecHours}
ggplot(tags, aes(x = hour)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "black") +
  theme_minimal() +
  labs(title = "Detections by Hour of Day", x = "Hour", y = "Count")
```

### Transmitter counts

```{r transmitterCounts}
tags_sf |> 
  count(transmitter) |> 
  ggplot(aes(x = reorder(transmitter, -n), y = n)) +
  geom_col(fill = "steelblue", color = "black") +
  theme_minimal() +
  labs(title = "Detection Counts per Transmitter", x = "Transmitter", y = "Count") +
  coord_flip()
```

### Transmitter by receiver

```{r}
  ggplot(tags_sf, aes(x = stationName, y = transmitter)) +
    geom_tile(aes(fill = ..count..), stat = "bin2d") +
    scale_fill_viridis_c() +
    theme_minimal() +
    labs(title = "Frequency of Transmitter Detections at Receivers",
         x = "Receiver",
         y = "Trasmitter",
         fill = "Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Creel Survey {.tabset}

```{r get_creel_data}
query <- "SELECT * FROM creelFishDetails"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelFishDetails<-fetch(result, -1)
dbClearResult(result)

query <- "SELECT * FROM creelFishResults"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelFishResults<-fetch(result, -1)
dbClearResult(result)

query <- "SELECT * FROM creelFisherDemography"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelFisherDemography<-fetch(result, -1)
dbClearResult(result)

query <- "SELECT * FROM creelShifts"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelShifts<-fetch(result, -1)
dbClearResult(result)

query <- "SELECT * FROM creelSurveyAnswers"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelSurveyAnswers<-fetch(result, -1)
dbClearResult(result)

query <- "SELECT * FROM creelSurveyQuestions"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelSurveyQuestions<-fetch(result, -1)
dbClearResult(result)

query <- "SELECT * FROM creelWeather"
dbExecute(con = con, query)
result <- dbSendQuery(conn = con, query)
creelWeather<-fetch(result, -1)
dbClearResult(result)


```

### Creel Shifts

```{r creel_shift_starts}
creelShifts %>%
  group_by(surveyor) %>%
  summarize(total_hours = sum(hours_worked)) %>%
  ggplot(aes(x = reorder(surveyor, -total_hours), y = total_hours, fill = surveyor)) + 
  geom_col() + 
  coord_flip() + 
  theme_minimal() + 
  labs(title = "Total Hours Worked by Surveyor", x = "Surveyor", y = "Total Hours")

ggplot(creelShifts, aes(x = as.integer(hours_worked))) +  # Ensure integer values
  geom_bar(fill = "orange", alpha = 0.6) + 
  scale_x_continuous(breaks = seq(min(creelShifts$hours_worked, na.rm = TRUE), 
                                  max(creelShifts$hours_worked, na.rm = TRUE), 
                                  by = 1)) +  # Ensure each integer has a tick mark
  theme_minimal() + 
  labs(title = "Distribution of Hours Worked per Shift", x = "Hours Worked", y = "Count")

```


```{r creelFishingResults}

summary(creelFishResults)

merged_data<- creelFishResults |> 
  left_join(creelFisherDemography, by = c("date", "surveyNumber"))

merged_data_2<- merged_data |> 
  left_join(creelFishDetails, by = c("date", "surveyNumber"))



creel_survey_responses<- creelSurveyAnswers |> 
  left_join(creelSurveyQuestions, by = "questionID")

wideanswers<- creel_survey_responses |> 
  select(-questionID) |> 
  pivot_wider(names_from = question, values_from = answer)
# 
# merged_big<- merged_data_2 |> 
#   left_join(creelSurveyAnswers, by = c("date", "surveyNumber"))
# 
# merged_big <- merged_big |>
#   left_join(creelSurveyQuestions, by = "questionID")


```



