---
title: "Creel Survey Data Check"
output: 
  html_document:
    toc: true
    toc_depth: 2
    theme: cosmo
---

# Creel Survey Data {.tabset}

```{r load-clean-main, message=FALSE, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(readxl)
library(janitor)
library(lubridate)
library(hms)
library(purrr)
library(skimr)
library(knitr)
library(kableExtra)
library(dplyr)
library(plotly)
library(tidyr)
library(htmltools)
library(lubridate)
library(plotly)
library(patchwork)
source("scripts/utils/fix_col_names_f.R")

lan_folder <- "//sfp.idir.bcgov/S140/S40203/WFC AEB/General/2 SCIENCE - Invasives/SPECIES/Smallmouth Bass/Cultus lake/"

the_files <- c(list.files(c(
  # No raw files in 2023, we could add these in later
  #"//sfp.idir.bcgov/S140/S40203/WFC AEB/General/2 SCIENCE - Invasives/SPECIES/Smallmouth Bass/Cultus lake/2023 projects/Creel Surveys/Archived Creel Forms/",
  "//sfp.idir.bcgov/S140/S40203/WFC AEB/General/2 SCIENCE - Invasives/SPECIES/Smallmouth Bass/Cultus lake/2024 projects/Creel Surveys/Creel Survey forms 2024 (backup)/",
  "//sfp.idir.bcgov/S140/S40203/WFC AEB/General/2 SCIENCE - Invasives/SPECIES/Smallmouth Bass/Cultus lake/2025 projects/Creel Surveys/Archived Creel Forms/"
),
pattern = "*.xlsx", recursive = TRUE, full.names = TRUE),
"//sfp.idir.bcgov/S140/S40203/WFC AEB/General/2 SCIENCE - Invasives/SPECIES/Smallmouth Bass/Cultus lake/2023 projects/Creel Surveys/2023 SMB creel_final not edits.xlsx"
)

the_files <- the_files[!grepl("~$", the_files)] # Remove temp files

sheet_names <- readxl::excel_sheets(the_files[1])

files_read_l <- the_files |> 
  lapply(function(x) {
    all_sheets <- readxl::excel_sheets(x)
    all_sheets |> 
      purrr::map(~ {
        # read everything as text
        dat_text <- readxl::read_excel(x, sheet = .x, col_types = "text")
        
        # rename special columns as you had before
        names(dat_text)[names(dat_text) == "# SMB c...15"] <- "# SMB c"
        names(dat_text)[names(dat_text) == "# SMB c...23"] <- "# SMB r"
        
        # clean names
        janitor::clean_names(dat_text)
      }) |> purrr::set_names(all_sheets)
  })

files_read_f <- list_flatten(files_read_l)



sheets_combined <- sheet_names |> 
  map(~ {
    files_read_f[which(names(files_read_f) == .x)] |> 
      bind_rows()
  })

names(sheets_combined) <- sheet_names

main <- sheets_combined$`Main Data`

# main page contains the same survey number and date - we should only keep one when this combo is the same

# Cleaning main data
main <- main |> 
  mutate(date = as.Date(as.numeric(date), origin = "1899-12-30")) |> 
  group_by(survey_number, date, time) |>
  fill(everything(), .direction = "downup") |>  # fill missing values in group
  slice_head(n = 1) |>                          # keep just the first row
  ungroup() |> 
  mutate(date = as.character(date)) |> 
  arrange(date) |> 
  group_by(as.character(date)) |> 
  mutate(survey_number = row_number()) |>  
  ungroup() |> 
  select(-`as.character(date)`) |> 
  mutate(
    date = as.character(date),
    time = hms::as_hms(as.numeric(time) %% 1 * 86400)
  ) |>
  group_by(time) |> 
  mutate(
    time = if_else(
      row_number() > 1,
      hms::as_hms(as.numeric(time) + 5 * 60 * (row_number() - 1)),
      time
    )
  ) |> 
  ungroup() |> 
  mutate(time = as.character(time)) |> 
  mutate(
    shift = str_remove(shift, "^\\d+: "),
    shift_end = sub(".*-", "", shift),
    shift_start = sub("-.*", "", shift),
    shift_start = if_else(str_detect(shift_start, "^\\d{1,2}:\\d{2}$"), paste0(shift_start, ":00"), shift_start),
    shift_end = if_else(str_detect(shift_end, "^\\d{1,2}:\\d{2}$"), paste0(shift_end, ":00"), shift_end),
    shift_start_time = hms::parse_hms(shift_start),
    shift_end_time = hms::parse_hms(shift_end),
    hours_worked = as.numeric(difftime(shift_end_time, shift_start_time, units = "hours")),
    shift_start_time = paste(date, shift_start_time),
    shift_end_time = paste(date, shift_end_time)
  )



main <- main |> 
  relocate(shift_end:hours_worked, .before = everything())

main <- main |> 
  mutate(
    wind = case_when(
      suppressWarnings(!is.na(as.numeric(wind))) ~ {
        date_val <- as.Date(as.numeric(wind), origin = "1899-12-30")
        paste0(month(date_val), "-", day(date_val))
      },
      TRUE ~ wind
    )
  )

main <- main |> 
  select(
    survey_number:total_fish_caught,
    number_smb_c:number_other_spp_c,
    number_pikeminnow_caught,
    total_retained,
    number_smb_r:number_other_spp_r,
    number_pikeminnow_r,
    everything()
  )

main <- main |> 
  mutate(
    air_temp = coalesce(air_temp, air_temperature, mean_air_temperature),
    wind = coalesce(wind, x44)
  ) |> 
  select(-c(air_temperature, x44))

main_page <- main[,1:37]

main_page <- main_page |> 
  rename(
    fishing_method = vessel,
    number_pikeminnow_c = number_pikeminnow_caught
  )

main_page <- main_page |> 
  filter(!is.na(date))

main_page<- main_page |> 
  relocate(shift_end:hours_worked, .after = everything())

```

## Main Data Table

Comparison of fish reported by year. "C" is the fish caught, and "R" are those that were retained.

```{r fish_caught}
counted <- main_page |>
  mutate(year = year(as.Date(date))) |>  
  group_by(year) |> 
  summarise(across(
    .cols = c(matches("^number.*[cr]$"), any_of(c("total_fish_caught", "total_fish_retained"))),
    .fns = ~ sum(as.numeric(.x), na.rm = TRUE),
    .names = "sum_{.col}"
  )) |> 
  rename_with(
    ~ str_remove_all(.x, "^sum_|^number_|^total_"),
    .cols = -year
  ) |> 
  as_tibble()

counted <- counted |>
  rename_with(
    ~ str_remove_all(.x, "^sum_|^number_|^total_"),
    .cols = -year
)


main_t_totals_long <- counted |>
  pivot_longer(
    cols = -year,                
    names_to = "metric",
    values_to = "total"
  )



library(ggplot2)
ggplot(main_t_totals_long, aes(x = metric, y = total, fill = factor(year))) +
  geom_col(position = position_dodge(width = 0.8)) +
  labs(
    x = "Species, Caught and Retained",
    y = "Total Count",
    fill = "Year"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)
  )


```


There are discrepancies in the total caught and total retained, versus the counts by species. I would assume this is due to surveying methods, getting a total count from an angler, but not getting to species level. I do not think this is a major consequence, but should probably be highlighted when using these data.

Chceking retained counts:

```{r}
retained_cols <- grep("^number.*_r$", names(main_page), value = TRUE)

retained_by_year <- main_page %>%
  mutate(year = year(as.Date(date))) %>%
  group_by(year) %>%
  summarise(
    retained_component_by_spp = sum(rowSums(across(all_of(retained_cols), ~ as.numeric(.x)), na.rm = TRUE)),
    reported_total_retained = sum(as.numeric(total_retained), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    difference_retained = retained_component_by_spp - reported_total_retained
  )

knitr::kable(retained_by_year)

```


Checking caught counts:

```{r}
caught_cols <- grep("^number.*_c$", names(main_page), value = TRUE)

caught_by_year <- main_page %>%
  mutate(year = year(as.Date(date))) %>%
  group_by(year) %>%
  summarise(
    caught_component_by_spp = sum(rowSums(across(all_of(caught_cols), ~ as.numeric(.x)), na.rm = TRUE)),
    reported_total_caught = sum(as.numeric(total_fish_caught), na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    difference_caught = caught_component_by_spp - reported_total_caught
  )

knitr::kable(caught_by_year)
```



## Fishing Effort

```{r fish-effort}

fishing_effort<- main_page |> 
  mutate(year = year(as.Date(date))) |>  
  group_by(year) |> 
  summarise( number_rods_year = sum(as.numeric(number_rods), na.rm = TRUE),
             total_person_hr_fished_year = sum(as.numeric(total_person_hr_fished ), na.rm = TRUE))
  
knitr::kable(fishing_effort, caption = "Fishing Effort by Year", digits = 2)


```


## Angling - Plots {.tabset}

### Anglers and fish caught/retained

The number of anglers - which I have assumed to be the number of anglers being surveyed.

The number of fish reported as "c" = caught, and "r" = retained. 

```{r number fish caught, fig.width=10, fig.height=8}

source("scripts/utils/func_plotly.R")


numbers <- main_page %>% 
  select(c(date, starts_with("number"))) %>% 
  select(-number_anglers, -number_rods) %>%   # remove unwanted columns
  rename_with(~ str_remove_all(.x, "^sum_|^number_|^total_")) %>% 
  mutate(across(-date, as.numeric)) %>% 
  as_tibble()

numbers_long <- numbers %>%
  pivot_longer(-date, names_to = "variable", values_to = "value")

plots <- numbers_long %>%
  mutate(date = as.Date(date)) %>%
  split(.$variable) %>% 
  map(~ {
    # keep dates where value is not NA
    valid_dates <- .x %>%
      filter(!is.na(value)) %>%
      pull(date) %>%
      unique()
    
    p <- ggplot(.x, aes(x = date, y = value)) +
      geom_point() +
      ggtitle(unique(.x$variable)) +
      theme_minimal()
    
    if (all(is.na(.x$value))) {
      p <- p + theme(
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank()
      )
    } else {
      p <- p +
        scale_x_date(date_labels = "%Y-%m-%d", breaks = scales::breaks_pretty(n = 6))
        theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 7))
    }
    
    ggplotly(p)
  })

walk(plots, print)

# Ensure numeric and extract year
fish_data <- main_page %>%
  select(date, total_fish_caught) %>%
  mutate(
    total_fish_caught = as.numeric(total_fish_caught),
    date = as.Date(date),
    year = format(date, "%Y")
  )

# Global ymax so y-axis is consistent across plots
ymax <- max(fish_data$total_fish_caught, na.rm = TRUE)

# Split by year and map to plots
plots <- fish_data %>%
  split(.$year) %>%
  map(~ {
    p <- ggplot(.x, aes(x = date, y = total_fish_caught)) +
      geom_bar(stat = "identity", fill = "steelblue") +
      theme_minimal() +
      labs(
        x = "Date",
        y = "Total Fish Caught",
        title = paste("Total Fish Caught in", unique(.x$year))
      ) +
      scale_x_date(date_labels = "%d %b %Y", date_breaks = "1 week") +
      scale_y_continuous(limits = c(0, ymax)) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    
    ggplotly(p)
  })

# Show all plots
walk(plots, print)


# Prepare your data
fish_data <- main_page %>%
  select(date, total_retained) %>%
  mutate(
    total_retained = as.numeric(total_retained),
    date = as.Date(date),
    year = format(date, "%Y")
  )

# Global y-axis max
ymax <- max(fish_data$total_retained, na.rm = TRUE)

# Split into list of plots per year
plots <- fish_data %>%
  split(.$year) %>%
  map(~ {
    p <- ggplot(.x, aes(x = date, y = total_retained)) +
      geom_bar(stat = "identity", fill = "steelblue") +
      theme_minimal() +
      labs(
        x = "Date",
        y = "Total Fish Retained",
        title = paste("Total Fish Retained in", unique(.x$year))
      ) +
      scale_x_date(date_labels = "%d %b %Y", date_breaks = "1 week") +
      scale_y_continuous(limits = c(0, ymax)) +
      theme(axis.text.x = element_text(angle = 45, hjust = 1))
    
    ggplotly(p)
  })

# Display each plot
walk(plots, print)


```

### Hours worked

```{r hours_worked}

hours_worked <- main_page |> 
  select(date, hours_worked) |> 
  mutate(across(-date, as.numeric))


# Make sure shift_start is a time/datetime
shifts <- main_page %>%
  mutate(
    shift_start = as_hms(shift_start),
    shift_end = as_hms(shift_end),
    shift_type = case_when(
      hour(shift_start) >= 6 & hour(shift_start) < 12 ~ "Morning",
      hour(shift_start) >= 12 & hour(shift_start) < 18 ~ "Afternoon",
      hour(shift_start) >= 18 & hour(shift_start) < 24 ~ "Evening",
      TRUE ~ "Other"
    ),
    # set factor levels to control order in plot
    shift_type = factor(shift_type, levels = c("Morning", "Afternoon", "Evening", "Other"))
  )

# Count shifts by type
shift_summary <- shifts %>%
  count(shift_type)

# Plot
ggplot(shift_summary, aes(x = shift_type, y = n, fill = shift_type)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    x = "Shift Type",
    y = "Number of Shifts",
    title = "Number of Shifts by Shift Type"
  ) +
  theme(legend.position = "none")

```



```{r questions_answers}


questionTables<-main|> 
  colnames()

questionTables <- questionTables |> 
  as.data.frame() |> 
  slice(38:54) |> 
  mutate(questionID = row_number()) |> 
  rename(question = questionTables)


answersTable<- main |> 
  select(c(survey_number, date, time, any_of(questionTables$question)))

answersLong <- answersTable |> 
  pivot_longer(cols = -c(survey_number, time, date), names_to = "Question", values_to = "Answer") |> 
  left_join(questionTables, by = c("Question" = "question")) |> 
  mutate(Question = questionID) |> 
  select(-questionID) |> 
  rename( surveyNumber = survey_number, date = date, time = time, questionID = Question, answer = Answer) |> 
  mutate(time = as.character(time))

answersLong<- answersLong |> 
  mutate(date = as.Date(date)) |> 
  arrange(date) |> 
  mutate(date_group = cumsum(date != lag(date, default = first(date)))) |> 
  # group_by(date_group) |> 
  # mutate(surveyNumber = row_number()) |>  
  # ungroup() |> 
  select(-date_group) |> 
  mutate(date = as.character(date))


answersLong <- answersLong |> 
  mutate(date = as.character(date))

```



## Demography {.tabset}

### Age classes


```{r demo}

demo_data <- sheets_combined$`Demographic Data`

age_summary <- demo_data %>%
  count(age_class)
  
# Make age_class an ordered factor so bars appear in logical order
age_summary <- age_summary %>%
  mutate(age_class = factor(age_class, levels = c("<16", "16-65", ">65"))) |> 
  filter(!is.na(age_class))

# Bar plot
ggplot(age_summary, aes(x = age_class, y = n, fill = age_class)) +
  geom_bar(stat = "identity") +
  theme_minimal() +
  labs(
    x = "Age Class",
    y = "Count",
    title = "Counts of Individuals by Age Class"
  ) +
  theme(legend.position = "none")


```

```{r city_province_country}


demo_data <- demo_data %>%
  mutate(
    # Normalize to uppercase and trim spaces
    city_prov_country = str_to_upper(str_trim(city_prov_country)),
    
    # Fix simple typos for BC
    city_prov_country = str_replace_all(city_prov_country, "^BC$|^BC\\.$|^BC$", "BC, Canada"),
    
    # Standardize other provinces/states/countries
    city_prov_country = case_when(
      city_prov_country %in% c("ON", "ONTARIO") ~ "Ontario, Canada",
      city_prov_country %in% c("AB") ~ "Alberta, Canada",
      city_prov_country %in% c("SASK", "SASKATCHEWAN") ~ "Saskatchewan, Canada",
      city_prov_country %in% c("FL", "FLORIDA") ~ "Florida, USA",
      city_prov_country %in% c("CALIFORNIA") ~ "California, USA",
      city_prov_country %in% c("UKRAINE") ~ "Ukraine",
      city_prov_country %in% c("THAILAND") ~ "Thailand",
      TRUE ~ city_prov_country
    ),
    
    # Combine common BC cities with province
    city_prov_country = case_when(
      city_prov_country %in% c("VANCOUVER", "METRO VANCOUVER", "NORTH VANCOUVER") ~ "Vancouver, BC, Canada",
      city_prov_country == "SURREY" ~ "Surrey, BC, Canada",
      city_prov_country == "BURNABY" ~ "Burnaby, BC, Canada",
      city_prov_country == "CHILLIWACK" ~ "Chilliwack, BC, Canada",
      city_prov_country == "LANGLEY" ~ "Langley, BC, Canada",
      city_prov_country == "ABBOTSFORD" ~ "Abbotsford, BC, Canada",
      city_prov_country == "WHITE ROCK" ~ "White Rock, BC, Canada",
      city_prov_country == "MAPLE RIDGE" ~ "Maple Ridge, BC, Canada",
      city_prov_country == "YARROW" ~ "Yarrow, BC, Canada",
      city_prov_country == "CULTUS" ~ "Cultus, BC, Canada",
      city_prov_country == "ROSEDALE" ~ "Rosedale, BC, Canada",
      city_prov_country == "COQUITLAM" ~ "Coquitlam, BC, Canada",
      city_prov_country == "EDMONTON" ~ "Edmonton, AB, Canada",
      city_prov_country == "VANCOUVER ISLAND" ~ "Vancouver Island, BC, Canada",
      city_prov_country == "NORTH VAN" ~ "Vancouver, BC, Canada",
      city_prov_country == "CULTUS LAKE" ~ "Cultus Lake, BC, Canada",
      city_prov_country == "VICTORIA" ~ "Victoria, BC, Canada",
      city_prov_country == "RICHMOND" ~ "Richmond, BC, Canada",
      city_prov_country == "NEW WESTMINSTER" ~ "New Westminster, BC, Canada",
      city_prov_country == "SLOCAN" ~ "Slocan, BC, Canada",
      city_prov_country == "DELTA" ~ "Delta, BC, Canada",
      city_prov_country == "ALDERGROVE" ~ "Aldergrove, BC, Canada",
      city_prov_country == "WALNUT GROVE" ~ "Walnut Grove, BC, Canada",
      city_prov_country == "US, NORTH CAROLINA" ~ "North Carolina, US",
      city_prov_country == "ST ALBERT, ALBERTA" ~ "St Albert, AB, Canada",
      city_prov_country == "SANTA BARBARA, CALIFORNIA" ~ "Santa Barbara, CA, US",
      city_prov_country == "PORTMOODY" ~ "Port Moody, BC, Canada",
      city_prov_country == "COQUITLAM" ~ "Coquitlam, BC, Canada",
      city_prov_country == "NEWWESTMINSTER" ~ "New Westminster, BC, Canada",
      city_prov_country == "MISSION" ~ "Mission, BC, Canada",
      city_prov_country == "KAMLOOPS" ~ "Kamloops, BC, Canada",
      city_prov_country == "CLOVERDALE" ~ "Surrey, BC, Canada",
      city_prov_country == "CACHE CREEK" ~ "Cache Creek, BC, Canada",
      city_prov_country == "PORT MOODY" ~ "Port Moody, BC, Canada",
      city_prov_country == "PROMONTORY" ~ "Promontory, BC, Canada",
      
      
      TRUE ~ city_prov_country
    ),
    
    # Create high-level region grouping
    region_group = case_when(
      str_detect(city_prov_country, "BC, Canada") ~ "BC",
      str_detect(city_prov_country, "Canada") ~ "Other Canada",
      TRUE ~ "International"
    )
  )


### Locations from inside BC
bc_data <- demo_data %>%
  filter(region_group == "BC")

### Locations outside BC, within Canada
canada_data <- demo_data %>%
  filter(region_group == "Other Canada")

### International Respondents
international_data <- demo_data %>%
  filter(region_group == "International")

```

### Locations from inside BC

```{r BC_location}
bc_data <- demo_data %>%
  filter(str_detect(city_prov_country, "BC"))

# Clean up BC city/region names
bc_data <- bc_data %>%
  mutate(city_clean = str_to_title(city_prov_country),   # capitalize properly
         city_clean = str_replace_all(city_clean, "Bc", "BC"),
         city_clean = str_replace_all(city_clean, "White Rock", "White Rock"),
         city_clean = str_replace_all(city_clean, "Metro Vancouver", "Vancouver"),
         city_clean = str_replace_all(city_clean, "Vancouver", "Vancouver"),
         city_clean = str_trim(city_clean)
  )

# Count respondents per city
bc_counts <- bc_data %>%
  count(city_clean, sort = TRUE)

# Plot
ggplot(bc_counts, aes(x = reorder(city_clean, n), y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Respondents from BC by City/Region", x = "City/Region", y = "Count") +
  theme_minimal()

```

### Locations outside BC, within Canada

```{r canadians}
canada_data <- demo_data %>%
  filter(!is.na(city_prov_country)) %>%
  filter(!str_detect(city_prov_country, "BC")) |> 
  filter(str_detect(city_prov_country, "Canada"))

# Count respondents per province
canada_counts <- canada_data %>%
  mutate(province = str_to_upper(city_prov_country)) %>%
  count(province, sort = TRUE)

# Plot
ggplot(canada_counts, aes(x = reorder(province, n), y = n)) +
  geom_bar(stat = "identity", fill = "forestgreen") +
  coord_flip() +
  labs(title = "Respondents from Canadian Provinces (excluding BC)", x = "Province", y = "Count") +
  theme_minimal()
```

### International Respondents

```{r internationals}
international_data <- demo_data %>%
  filter(!is.na(city_prov_country)) %>%
  filter(!str_detect(city_prov_country, "Canada"))

# Count respondents per province
international_counts <- international_data %>%
  mutate(province = str_to_upper(city_prov_country)) %>%
  count(province, sort = TRUE)

# Plot
ggplot(international_counts, aes(x = reorder(province, n), y = n)) +
  geom_bar(stat = "identity", fill = "darkred") +
  coord_flip() +
  labs(title = "International Respondents", x = "Location", y = "Count") +
  theme_minimal()
```



## Fish data {.tabset}

### Fish length vs weight


```{r load_fish} 
# Filter out rows without date_time and create date/time columns
fish <- sheets_combined$`Fish Data` %>%
  mutate(temp = coalesce(pit_tag_number, p_it_tag_number)) %>%
  # Remove the old columns
  select(-pit_tag_number, -p_it_tag_number) %>%
  # Rename the temp column to the standardized name
  rename(pit_tag_number = temp) |>
  filter(!is.na(date_time)) %>%
  mutate(
    date = as.Date(as.numeric(date_time), origin = "1899-12-30"),
    time = hms::as_hms(as.numeric(date_time) %% 1 * 86400)
  ) %>%
  select(-date_time)

fish = fish |> 
  mutate(spp = case_when(spp %in% c("Lrg Scl Suckr", "Lrg Scale Suckr") ~ "Large Scale Sucker",
                         spp %in% c("Pumpkin sedd", "PS") ~ "Pumpkinseed",
                         spp %in% c("RT") ~ "Rainbow Trout",
                         spp %in% c("SMB") ~ "Smallmouth Bass",
                         TRUE ~ spp))
  

# Clean and prepare data
fish_clean <- fish %>%
  mutate(
    length_mm = as.numeric(length_mm),
    weight_g = as.numeric(weight_g)
  )

# Create ggplot
p <- ggplot(fish_clean, aes(x = length_mm, y = weight_g, color = spp, text = paste(
  "Survey:", survey_number,
  "<br>Fish #:", fish_number,
  "<br>Species:", spp,
  "<br>Length (mm):", length_mm,
  "<br>Weight (g):", weight_g,
  "<br>Date:", date
))) +
  geom_point(size = 2, alpha = 0.8) +
  theme_minimal() +
  labs(
    title = "Fish Length vs Weight by Species",
    x = "Length (mm)",
    y = "Weight (g)",
    color = "Species"
  )

# Convert to interactive Plotly plot
ggplotly(p, tooltip = "text")

```



## ICE {.tabset}

```{r ice_data}

ICE<- sheets_combined$ICE

ICE_long <- ICE |> 
  mutate(date = as.Date(as.numeric(date), origin = "1899-12-30")) |> 
   # Combine the two columns into a temporary one
  mutate(temp = coalesce(air_temp, air_temperature)) %>%
  # Remove the old columns
  select(-air_temp, -air_temperature) %>%
  # Rename the temp column to the standardized name
  rename(air_temperature = temp) |>
  mutate(temp = coalesce(precip, precipitation)) %>%
  # Remove the old columns
  select(-precip, -precipitation) %>%
  # Rename the temp column to the standardized name
  rename(precipitation = temp) |>
  mutate(across(everything(), as.character)) %>%
  pivot_longer(
    cols = -c(date, time),       # keep date and time
    names_to = "variable",
    values_to = "value"
  ) %>%
  group_by(variable) %>%
  group_split()

```

```{r get_ice_plots}
# Combine your list of tibbles into one data frame
ICE_all <- ICE_long %>%
  bind_rows() %>%
  mutate(
    date = as.Date(date),
    time = as.numeric(time),
    value = suppressWarnings(as.numeric(value)),  # avoid warnings from NAs
    year = year(date)
  ) %>%
  arrange(variable, date, time)

# Get all unique variable names
variables <- unique(ICE_all$variable)

# Create a nested list of plots: plots[[variable]][[year]]
plots <- map(variables, function(v) {
  df <- ICE_all %>% filter(variable == v)
  years <- sort(unique(df$year))

  map(years, function(y) {
    df_y <- df %>% filter(year == y)

    plot_ly(
      data = df_y,
      x = ~date,
      y = ~value,
      type = "scatter",
      mode = "lines+markers",
      name = paste(v, y),
      hoverinfo = "text",
      text = ~paste(
        "Date:", date,
        "<br>Time:", time,
        "<br>Value:", value
      )
    ) %>%
      layout(
        title = paste("Variable:", v, "-", y),
        xaxis = list(title = "Date"),
        yaxis = list(title = "Value")
      )
  }) %>%
    set_names(years)
}) %>%
  set_names(variables)
```


```{r plot_air_temp}

#plots$weather

```

### Air Temperature

```{r }
plots$air_temperature$`2023`
plots$air_temperature$`2024`
plots$air_temperature$`2025`



```

### Cloud Cover

```{r }
plots$cloud_cover$`2023`
plots$cloud_cover$`2024`
plots$cloud_cover$`2025`
```


```{r }

#plots$precipitation

```

### Angling Boats

```{r }
plots$number_angling_boats$`2023`

plots$number_angling_boats$`2024`

plots$number_angling_boats$`2025`

```

###  Dock Anglers
```{r }
plots$number_dock_anglers$`2023`

plots$number_dock_anglers$`2024`
plots$number_dock_anglers$`2025`

```


### Shore Anglers

```{r }

plots$number_shore_anglers$`2023`
plots$number_shore_anglers$`2024`
plots$number_shore_anglers$`2025`

```

### Number of Angling Boats

```{r }

plots$number_angling_boats$`2023`
plots$number_angling_boats$`2024`
plots$number_angling_boats$`2025`

```
